TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-09-19 paper/draft.tex
wording

Following from the procedure of \citealt{Ness:2015} and \citealt{Ho:2017a} we adopt a simple linear model that assumes the flux at each pixel of the spectrum can be parameterized as a function of a label vector $\ell_n$ and and coefficient vector \emph{$\theta$}. So for each star \emph{n}, at pixel wavelength \emph{$\lambda$}, we state that the measured flux for a star at a given pixel is the sum of the coefficient and label product, and observational noise:
\begin{equation}
	f_{n\lambda} = \theta_{\lambda}^{T} \cdot \ell_{n} + {\rm noise}
\end{equation}
We use the noise model is ${\rm noise}=[s_{\lambda}^2 + \sigma_{n\lambda}^2]\xi_{n\lambda}$, where the bracketed term is the root mean sum of the intrinsic scatter of the model at each pixel \emph{$s_{\lambda}$}, and the uncertainty due to instrumental effects \emph{$\sigma_{n\lambda}$}, which is then multiplied times a Gaussian random number $\xi_{n\lambda} \sim \mathcal{N} (0,1)$.

We apply a quadratic parameterization of the model such that the label vectors for the two models are all of the combinations of reference labels, up to second order:
\begin{eqnarray}
\ell_{n} &=& [1, \, SPT, \, SPT^{2}] \label{eqn:spt}
\\
\ell_{n} &=& [1, \, T_{\rm eff}, \, [Fe/H], \, T_{\rm eff}^2, \, T_{\rm eff} \cdot [Fe/H], \, [Fe/H]^{2}] \label{eqn:physical}
,
\end{eqnarray}
Equation (\ref{eqn:spt}) is the label vector for the spectral type model, and equation (\ref{eqn:physical}) is the label vector for the physical parameter model, and the first element ``1'' is included to allow flexibility for a linear offset to the model. We find that a second order parameterization is sufficient for describing the flux of each spectrum to one percent accuracy, as discussed further in Section \ref{subsec:mann_results}.

The \emph{training step} consists of optimizing for the coefficient vector and scatter ($\theta_{\lambda}$ and $s_{\lambda}$) at fixed labels (\emph{$\ell_n$}), and the \emph{test step} consists of optimizing for labels at fixed $\theta_{\lambda}$ and scatter.

>>>>

Following from the procedure of \citealt{Ness:2015} and \citealt{Ho:2017a} we adopt a simple linear model that assumes the flux at each pixel of the spectrum can be parameterized as a function of a label vector $\ell$ and and coefficient vector \emph{$\theta$}. So for each star \emph{n}, at pixel wavelength \emph{$\lambda$}, we state that the measured flux for a star at a given pixel is the sum of the coefficient and label product, and observational noise:
\begin{equation}
	f_{n\lambda} = \theta_{\lambda}^{T} \cdot \ell_{n} + {\rm noise}
\end{equation}
We use the noise model is ${\rm noise}=[s_{\lambda}^2 + \sigma_{n\lambda}^2]\xi_{n\lambda}$, where the bracketed term is the root mean sum of the intrinsic scatter of the model at each pixel \emph{$s_{\lambda}$}, and the uncertainty due to instrumental effects \emph{$\sigma_{n\lambda}$}, which is then multiplied times a Gaussian random number $\xi_{n\lambda} \sim \mathcal{N} (0,1)$.

We apply a quadratic parameterization of the model such that the label vectors for the two models are all of the combinations of reference labels, up to second order:
\begin{eqnarray}
\ell_{n} &=& [1, \, SPT, \, SPT^{2}] \label{eqn:spt}
\\
\ell_{n} &=& [1, \, T_{\rm eff}, \, [Fe/H], \, T_{\rm eff}^2, \, T_{\rm eff} \cdot [Fe/H], \, [Fe/H]^{2}] \label{eqn:physical}
,
\end{eqnarray}
Equation (\ref{eqn:spt}) is the label vector for the spectral type model, and equation (\ref{eqn:physical}) is the label vector for the physical parameter model, and the first element ``1'' is included to allow flexibility for a linear offset to the model. We find that a second order parameterization is sufficient for reproducing the flux of each spectrum to one percent accuracy, as discussed further in Section \ref{subsec:mann_results}.

The \emph{training step} consists of optimizing for the coefficient vector and scatter ($\theta_{\lambda}$ and $s_{\lambda}$) given fixed label vector (\emph{$\ell_n$}), and the \emph{test step} consists of optimizing for the labels at fixed $\theta_{\lambda}$ and $s_{\lambda}$.
